---
title: "Data Processing"
author: "Carson Weaver"
date: "2/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, echo=FALSE, warnings=FALSE, include=FALSE}
library(dplyr)
library(ggplot2)
library(png)
library(RSpectra)
library(Matrix)
set.seed(100)
```

TODO: Generate list of files used in training set, right join with original set on names.

```{r parameters}
leaf_img_side_length <- 100
```

Standardize the sizes of the photos from the training set.

```{r resize_photos} 

source <- paste0(getwd(), "/../data/revision_1")
destination <- paste0(getwd(), "/../data/", "training_set_", leaf_img_side_length, "x", leaf_img_side_length)

if (dir.exists(destination)) {
  print("Already exists.")
} else {
  create_new_test_set = paste0(getwd(), 
                               "/../utils/resize_images.bat", " ", 
                               leaf_img_side_length, " \"", 
                               source, "\" \"", 
                               destination, "\"")
  shell(create_new_test_set)
}

```

Assemble the data matrix, with each row being the pixel data from a single photo.

```{r assemble_matrix, echo = FALSE}
destination <- paste0(getwd(), "/../data/", "training_set_", leaf_img_side_length, "x", leaf_img_side_length)
manifest <- list.files(destination, full.names = TRUE)

pixel_matrix <- matrix(nrow = length(manifest), ncol = leaf_img_side_length^2)
pixel_matrix <- as(pixel_matrix, "dgCMatrix")
for (i in 1:length(manifest)) {
  photo_data <- readPNG(manifest[[i]])
  pixel_matrix[i,] <- c(photo_data)
  print(i)
}
rm(photo_data)

name <- paste0("../data/pixel_matrix_", leaf_img_side_length, "x", leaf_img_side_length, ".RDS")
saveRDS(pixel_matrix, file = name)
rm(pixel_matrix)
```

Generate covariance matrix for leaf photo data.

```{r get_covariance_matrix}
name <- paste0("../data/pixel_matrix_", leaf_img_side_length, "x", leaf_img_side_length, ".RDS")
pixel_matrix <- readRDS(name)

ones_mat <- data.frame(matrix(data = 1,nrow=length(manifest), ncol=length(manifest) - 1))
ones_mat <- sparse.model.matrix(~ ., data = ones_mat)

intermediate <- pixel_matrix - ((ones_mat %*% pixel_matrix) * (1 / leaf_img_side_length))
rm(pixel_matrix)
rm(ones_mat)
covar_mat <- (t(intermediate) %*% intermediate) * (1 / leaf_img_side_length)

name <- paste0("../data/covar_matrix_", leaf_img_side_length, "x", leaf_img_side_length, ".RDS")
saveRDS(covar_mat, name)
rm(covar_mat)
```

Get the eigenvectors of covariance matrix associated with the n_values, the principal components of the dataset.

```{r get_eigenvectors}
name <- paste0("../data/covar_matrix_", leaf_img_side_length, "x", leaf_img_side_length, ".RDS")
covar_mat <- readRDS(name)

n_values <- 5
eig_object <- eigs_sym(covar_mat, k = n_values, which = "LM")
rm(covar_mat)
```

Save the principal components as images to the hard drive.

```{r vector_to_picture}
for (i in 1:n_values) {
  vec <- eig_object$vectors[,i]
  mat <- (matrix(vec, nrow = leaf_img_side_length, ncol = leaf_img_side_length) - mean(vec)) / sd(vec)
  path <- paste0("../data/PC-", i, "-img.png")
  writePNG(mat, target = path)
}
```

TODO: Get loadings of pixel matrix.
TODO: Make 2d/3d visualization of PCA.
